%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% This version has been modified by:
% Sebastian Dziadzio (sebastian.dziadzio@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\PassOptionsToPackage{dvipsnames,svgnames}{xcolor}
\documentclass[]{friggeri-cv_osx}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage[]{hyperref}
\hypersetup{
    colorlinks=false,
    urlcolor=MidnightBlue,
}

\begin{document}

\header{Sebastian }{Dziadzio}{}
\vspace{5mm}
\begin{center}
\href{https://sebastiandziadzio.com}{\color{gray} \Large \faHome} \hspace{0.05cm}
\href{https://github.com/sebastiandziadzio}{\color{gray} \Large \faGithub} \hspace{0.05cm}
\href{https://twitter.com/sbdzdz}{\color{gray} \Large\faTwitter} \hspace{0.05cm}
\href{https://pl.linkedin.com/in/sebastiandziadzio}{\color{gray} \Large\faLinkedin} \hspace{0.05cm}
\href{https://scholar.google.com/citations?user=8vAIQXoAAAAJ&hl=en}{\color{gray} \Large\faGraduationCap} \hspace{0.05cm}
\end{center}
\vspace{2mm}

\section{Experience}
\begin{entrylist}
\entry
{2019–2021}
{Scientist, Microsoft Research, Mixed Reality \& AI Lab}
{Cambridge, United Kingdom}
{I worked on a parametric 3D face model that powered multiple projects across the team. I built the training, evaluation, and visualization infrastructure, developed new features, fixed bugs,
and lead a research effort that reduced the average fit error by half. I~worked with PyTorch, TensorFlow, and NumPy.\\}

\entry
{2018–2019}
{AI Resident, Microsoft Research}
{Cambridge, United Kingdom}
{I worked on deep generative models for novel view synthesis and on deep reinforcement learning for video games. Both projects involved
formulating research questions, implementing and extending existing methods, and presenting the results at internal conferences. I used Pytorch, C\#, and OpenCV.\\}

\entry
{2016–2018}
{Data Scientist, Cliqz}
{Munich, Germany}
{I~implemented an information retrieval model combining LSTM networks and CNNs. I~also built a pipeline for
collecting, processing, and visualizing telemetry data. I worked with Python, TensorFlow, and Spark.\\}

\entry
{2015–2016}
{Software Engineer, Nokia Networks}
{Kraków, Poland}
{I was responsible for implementing new features for the LTE control plane, as well as designing unit tests, system component tests,
and integration tests. I~used C++ and Python.\\}

\end{entrylist}


\section{Education}
\begin{entrylist}

\entry
{2022–2026}
{PhD, Computer Science, University of Tübingen}
{Tübingen, Germany}
{I am a PhD student at the International Max Planck Research School for Intelligent Systems, working with Matthias Bethge and Tinne Tuytelaars in the ELLIS program. My main research interest is continual multimodal learning and lifelong benchmarking. Anticipated graduation date: 02/26.\\}

\entry
{2014–2016}
{MSc, Computer Science, AGH University}
{Kraków, Poland}
{Final grade: 5/5\\
Selected courses: machine learning, natural language processing, advanced algorithms and data structures, robotics, knowledge representation and reasoning.\\}

\entry
{2010–2014}
{BEng, Acoustical Engineering, AGH University}
{Kraków, Poland}
{Final grade: 4.5/5\\
Selected courses: algebra, calculus, physics, digital signal processing, speech technology, object-oriented system design, image processing, cognitive robotics.}
\end{entrylist}

\newpage
\section{Publications}
\begin{entrylist}

\entry
{2024}
{Democratizing Evaluation with $\infty$-Benchmarks: Sample-Level Heterogeneous Testing of Vision and Language Models Over Arbitrary Capabilities}
{}
{Adhiraj Ghosh*, Sebastian Dziadzio*, Ameya Prabhu, Vishal Udandarao, Samuel Albanie, Matthias Bethge.
\textit{In Review.}\\}

\entry
{2024}
{A Practitioner's Guide to Continual Multimodal Pretraining}
{}
{Karsten Roth*, Vishaal Udandarao*, Sebastian Dziadzio, Ameya Prabhu, Mehdi Cherti, Oriol Vinyals, Olivier Hénaff, Samuel Albanie, Matthias Bethge, Zeynep Akata.
\textit{NeurIPS Datasets and Benchmarks 2024.}\\}

\entry
{2024}
{\href{https://scholar.google.com/citations?user=8vAIQXoAAAAJ&hl=en}{Infinite dSprites for Disentangled Continual Learning: Separating Memory Edits from Generalization}}
{}
{Sebastian Dziadzio, Çağatay Yıldız, Gido M. van de Ven, Tomasz Trzciński, Tinne Tuytelaars, Matthias Bethge.
\textit{Proceedings of the Third Conference on Lifelong Learning Agents. PMLR, 2024.}\\}

\entry
{2023}
{\href{https://scholar.google.com/citations?user=8vAIQXoAAAAJ&hl=en}{Controllable Image Generation}}
{}
{Marek Kowalski, Stephan Garbin, Matthew Johson, Tadas Baltru\v{s}aitis, Martin De La Gorce, Virginia Estellers, Sebastian Dziadzio.
\textit{US Patent US-11748932.}\\}

\entry
{2023}
{\href{https://scholar.google.com/citations?user=8vAIQXoAAAAJ&hl=en}{Multiscale Neural Operators for Solving Time-Independent PDEs}}
{}
{Winfried Ripken, Lisa Coiffard, Felix Pieper, Sebastian Dziadzio.
\textit{NeurIPS 2023 Workshop on Deep Learning and Differential Equations.}\\}

\entry
{2022}
{\href{https://scholar.google.com/citations?user=8vAIQXoAAAAJ&hl=en}{Computing photorealistic versions of synthetic images}}
{}
{Stephan Garbin, Marek Kowalski, Matthew Johson, Tadas Baltru\v{s}aitis, Martin De La Gorce, Virginia Estellers, Sebastian Dziadzio, Jamie Shotton.
\textit{US Patent US-11354846.}\\}

\entry
{2021}
{\href{https://scholar.google.com/citations?user=8vAIQXoAAAAJ&hl=en}{Fake it Till You Make It: Face Analysis in the Wild Using Synthetic Data Alone}}
{}
{Tadas Baltru\v{s}aitis, Erroll Wood, Charlie Hewitt, Sebastian Dziadzio, Tom Cashman, Jamie Shotton.
\textit{Proceedings of the IEEE/CVF International Conference on Computer Vision.}\\}

\entry
{2021}
{\href{https://scholar.google.com/citations?user=8vAIQXoAAAAJ&hl=en}{Full-Body Motion from a Single Head-Mounted Device: Generating SMPL Poses from Partial Observations}}
{}
{Andrea Dittadi, Sebastian Dziadzio, Darren Cosker, Ben Lundell, Tom Cashman, Jamie Shotton.
\textit{Proceedings of the IEEE/CVF International Conference on Computer Vision.}\\}
\end{entrylist}

\section{Expertise}
\begin{entrylist}
\entry
{}
{Programming}
{}
{Python (PyTorch, TensorFlow, NumPy), C++}

\entry
{}
{Knowledge}
{}
{machine learning, continual multimodal learning, software development}

\entry
{}
{Skills}
{}
{public speaking, technical and scientific writing, agile project management}

\entry
{}
{Languages}
{}
{Polish (native), English (fluent), German (intermediate), Spanish (conversational)}
\end{entrylist}
\end{document}
